Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-13 analysis/paper/shceof.Rmd
Aumenta densidad de puntitos significantes

pattern_dots <- ggplot2::ggproto("GeomDots", ggpattern::GeomPolygonPattern)
ggplot2::update_geom_defaults(pattern_dots, 
                              list(pattern = "circle",
                                   colour = NA,
                                   pattern_colour = NA,
                                   pattern_fill = "black",
                                   pattern_density = 0.25,
                                   pattern_alpha = 0.5,
                                   pattern_spacing = 0.03,
                                   fill = NA
                              ))
update_geom_defaults(GeomSmooth, list(colour = "#0d52bf"))

>>>>

pattern_dots <- ggplot2::ggproto("GeomDots", ggpattern::GeomPolygonPattern)
ggplot2::update_geom_defaults(pattern_dots, 
                              list(pattern = "circle",
                                   colour = NA,
                                   pattern_colour = NA,
                                   pattern_fill = "black",
                                   pattern_density = 0.3,
                                   pattern_alpha = 1,
                                   pattern_spacing = 0.02,
                                   fill = NA
                              ))
update_geom_defaults(GeomSmooth, list(colour = "#0d52bf"))
